5'CutSiteAnalysisDataGeneration

### 2023-08-08 R/CutSiteCorrelationDataGeneration.rmd
Added no-position-filtering control

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteCorrelationAnalysisDataGeneration = function(lesion, repetition, timepoint, cellType, inputDirectory, outputDirectory,
                                                    includedMismatches = character(), omittedMismatches = character(),
                                                    filteredAndFormattedInput = TRUE,
                                                    filePathIncludedMismatches = NULL, filePathOmittedMismatches = NULL) {

@@

  if (filteredAndFormattedInput) {
    inputType = dataTypeStrings$mismatchesByReadRelationFormatted
  } else {
    inputType = dataTypeStrings$mismatchesByRead
  }

@@

  if (filteredAndFormattedInput) {
    additionalInformation = character()
  } else {
    additionalInformation = "minimal_filtering"
  }

@@

```{r generate_cut_site_correlation_data}
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         omittedMismatches = "C>T")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T", filteredAndFormattedInput = FALSE,
                                         filePathIncludedMismatches = character())
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         omittedMismatches = "C>T", filteredAndFormattedInput = FALSE,
                                         filePathOmittedMismatches = character())

>>>>

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteCorrelationAnalysisDataGeneration = function(lesion, repetition, timepoint, cellType, inputDirectory, outputDirectory,
                                                    includedMismatches = character(), omittedMismatches = character(),
                                                    filteredAndFormattedInput = TRUE, noPositionFiltering = FALSE,
                                                    filePathIncludedMismatches = NULL, filePathOmittedMismatches = NULL) {

@@

  if (filteredAndFormattedInput) {
    if (noPositionFiltering) {
      inputType = paste0(dataTypeStrings$mismatchesByReadRelationFormatted,"_no_position_filtering")
    } else {
      inputType = dataTypeStrings$mismatchesByReadRelationFormatted
    }
  } else {
    inputType = dataTypeStrings$mismatchesByRead
  }

@@

  if (filteredAndFormattedInput) {
    if (noPositionFiltering) {
      additionalInformation = "no_position_filtering"
    } else {
      additionalInformation = character()
    }
  } else {
    additionalInformation = "minimal_filtering"
  }

@@

```{r generate_cut_site_correlation_data}
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         omittedMismatches = "C>T")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T", filteredAndFormattedInput = FALSE,
                                         filePathIncludedMismatches = character())
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         omittedMismatches = "C>T", filteredAndFormattedInput = FALSE,
                                         filePathOmittedMismatches = character())
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT", noPositionFiltering = TRUE)
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T", noPositionFiltering = TRUE)

### 2023-08-08 R/CutSiteCorrelationFigureGeneration.rmd
Added no-position-filtering control

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteCorrelationAnalysisFigureGeneration = function(lesion, repetition, timepoint, cellType, directory,
                                                      includedMismatches = character(), omittedMismatches = character(),
                                                      filteredAndFormattedInput = TRUE, shuffle = FALSE) {

  if (filteredAndFormattedInput) {
    additionalInformation = character()
  } else {
    additionalInformation = "minimal_filtering"
  }

@@

cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T", filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           omittedMismatches = "C>T", filteredAndFormattedInput = FALSE)
```

>>>>

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteCorrelationAnalysisFigureGeneration = function(lesion, repetition, timepoint, cellType, directory,
                                                      includedMismatches = character(), omittedMismatches = character(),
                                                      filteredAndFormattedInput = TRUE, noPositionFiltering = FALSE,
                                                      shuffle = FALSE) {

  if (filteredAndFormattedInput) {
    if (noPositionFiltering) {
      additionalInformation = "no_position_filtering"
    } else {
      additionalInformation = character()
    }
  } else {
    additionalInformation = "minimal_filtering"
  }

@@

cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T", filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           omittedMismatches = "C>T", filteredAndFormattedInput = FALSE)

cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT", noPositionFiltering = TRUE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T", noPositionFiltering = TRUE)
```
